### 2016-12-31 README.Rmd
remove link to doi that doesn't render properly
upate readme shields [skip ci]

[![Build Status](https://travis-ci.org/lgatto/MSnbase.svg?branch=master)](https://travis-ci.org/lgatto/MSnbase) [![codecov.io](https://codecov.io/github/lgatto/MSnbase/coverage.svg?branch=master)](https://codecov.io/github/lgatto/MSnbase?branch=master)

@@

> Gatto L, Lilley KS. *`MSnbase` - an R/Bioconductor package for
> isobaric tagged mass spectrometry data visualization, processing and
> quantitation*. Bioinformatics. 2012 Jan
> 15;28(2):288-9. doi:[10.1093/bioinformatics/btr645](http://bioinformatics.oxfordjournals.org/content/28/2/288.long). Epub
> 2011 Nov 22.  PubMed
> [PMID:22113085](http://www.ncbi.nlm.nih.gov/pubmed/22113085).

>>>>

Travis-CI:
[![Build Status](https://travis-ci.org/lgatto/MSnbase.svg?branch=master)](https://travis-ci.org/lgatto/MSnbase) 
[![codecov.io](https://codecov.io/github/lgatto/MSnbase/coverage.svg?branch=master)](https://codecov.io/github/lgatto/MSnbase?branch=master)
Bioconductor:
[![Bioconductor devel build Status](http://bioconductor.org/shields/build/devel/bioc/MSnbase.svg)](http://bioconductor.org/packages/devel/bioc/html/MSnbase.html) 
[![Test coverage](https://bioconductor.org/shields/coverage/release/MSnbase.svg)](https://bioconductor.org/shields/coverage/devel/MSnbase.svg)

@@

> Gatto L, Lilley KS. *`MSnbase` - an R/Bioconductor package for
> isobaric tagged mass spectrometry data visualization, processing and
> quantitation*. Bioinformatics. 2012 Jan
> 15;28(2):288-9. doi:10.1093/bioinformatics/btr645. PubMed
> [PMID:22113085](http://www.ncbi.nlm.nih.gov/pubmed/22113085).
